Analytic Occultation Light Curves in Reflected Light

### 2020-04-02 tex/ms.tex
more texts

% Shorthand for this paper
\usepackage{xifthen}
\newcommand{\BF}[1]{\ensuremath{\mathbf{#1}}}
\newcommand{\BS}[1]{\ensuremath{\boldsymbol{#1}}}
\newcommand{\dd}{\ensuremath{\mathrm{d}}}
\newcommand{\STARRYQUADPOINTS}{100\xspace}
\newcommand{\bkappa}{\BS{\kappa}}
\newcommand{\blambda}{\BS{\lambda}}
\newcommand{\bxi}{\BS{\xi}}
\newcommand{\vmax}{{v_\mathrm{max}}}
\newcommand{\kapint}[1]{%
\sum_{i = 0}^{\frac{N - 1}{2}}
\int\limits_{\frac{1}{2}\kappa_{2i}}^{\frac{1}{2}\kappa_{2i+1}}
#1
\dd\varphi
}
\newcommand{\lamint}[1]{%
\sum_{i = 0}^{\frac{N - 1}{2}}
\int\limits_{\frac{1}{2}\lambda_{2i}}^{\frac{1}{2}\lambda_{2i+1}}
#1
\dd\varphi
}
\newcommand{\coshalfkap}[1][]{%
\ifthenelse{%
    \equal{#1}{}
}{
    \cos\left(\frac{\bkappa}{2}\right)
}{
    \cos^{#1}\left(\frac{\bkappa}{2}\right)
}}
\newcommand{\sinhalfkap}[1][]{%
\ifthenelse{%
    \equal{#1}{}
}{
    \sin\left(\frac{\bkappa}{2}\right)
}{
    \sin^{#1}\left(\frac{\bkappa}{2}\right)
}}
\newcommand{\DE}{\Delta \BS{E}(k^2, \bkappa)}
\newcommand{\DF}{\Delta \BS{F}(k^2, \bkappa)}
\newcommand{\sgn}{{\mathrm{sgn}}}
\newcommand{\xhat}{\ensuremath{\mathbf{\hat{x}}}\xspace}
\newcommand{\yhat}{\ensuremath{\mathbf{\hat{y}}}\xspace}
\newcommand{\zhat}{\ensuremath{\mathbf{\hat{z}}}\xspace}
\newcommand{\sT}{\ensuremath{\BF{s}^\top}}
\newcommand{\rT}{\ensuremath{\BF{r}^\top}}
\newcommand{\bg}{\ensuremath{\tilde{\BF{g}}}}
\newcommand{\bp}{\ensuremath{\tilde{\BF{p}}}}
\newcommand{\by}{\ensuremath{\tilde{\BF{y}}}}

@@

%
\section{The Problem}
\label{sec:the-problem}
%
\subsection{Review of the \starry algorithm in emitted light}
\label{sec:starry-review}
%
Without loss of generality, assume the body whose flux we wish to compute
has radius unity and sits at the origin of a right-handed Cartesian coordinate
system with the $x$-axis pointing to the right on the sky, the $y$-axis
pointing up on the sky, and the $z$-axis pointing out of the sky
toward the observer; denote this frame by $\mathcal{F}_0$. In $\mathcal{F}_0$,
the surface (emitted) intensity field of the body is described by the
spherical harmonic coefficient vector $\mathbf{y}$. Following
\citet{Luger2019}, when no occultor is present, we may compute the total
visible flux $f$ from this body as
%
\begin{align}
    \label{eq:rTA1Ry}
    f = \rT \BF{A_1} \BF{R} \BF{y}
    \quad,
\end{align}
%
where, from right to left, $\BF{R} = \BF{R}(i, \lambda, \vartheta)$
is a Wigner rotation matrix that rotates $\bvec{y}$ to the sky frame
$\mathcal{F}_\mathrm{sky}$ given the body's inclination $i$, obliquity
$\lambda$, and rotational phase $\vartheta$,
%
$\BF{A_1}$ is the change-of-basis matrix from the spherical harmonic
basis $\by$ to the \emph{polynomial basis} $\bp$ in which the integrals
are computed,
%
and $\rT$ is the vector of solutions to the integral over
the projected visible disk of the body for each term in $\bp$.
%
If an occultor is present, we instead compute the visible flux from
%
\begin{align}
    \label{eq:sTARRy}
    f = \sT \BF{A} \BF{R}' \BF{R} \BF{y}
    \quad,
\end{align}
%
where, as before, $\BF{R}$ rotates the body from $\mathcal{F}_0$
to $\mathcal{F}_\mathrm{sky}$,
%
$\BF{R}'$ rotates the body on the plane
of the sky into the frame $\mathcal{F}_\mathrm{greens}$ in which the
integration is actually performed,
%
$\BF{A}$ is the change-of-basis matrix from $\by$
to the \emph{Green's basis} $\bg$ in which the integrals are computed,
%
and $\sT$ is the vector of solutions to the integral over
the projected visible disk of the body for each term in $\bg$.
For more details, see Appendix~\ref{app:starry} and \citet{Luger2019}.

@@

body is illuminated by a point-like source, in which case the radiance at any

@@

of semi-major axis unity that is fully described by its semi-minor axis,

@@

    b = -\frac{z_s}{\sqrt{x_s^2 + y_s^2 + z_s^2}}

@@

@@

$x_s^2 + y_s^2 + z_s^2 \gg 1$,

@@

$I$ at a point $(x, y)$ on the projected disk of the body is given by
the polynomial

@@

    \frac{I(b, \theta; x, y)}{I_0} &=

@@

where $b_c = \sqrt{1 - b^2}$, $z(x, y) = \sqrt{1 - x^2 - y^2}$, and

@@

    I_0 = \frac{L}{4\pi\left(x_s^2 + y_s^2 + z_s^2\right)}

@@

is the peak illumination (at the substellar point,
assuming the illumination source is a star), with $L$ equal to the luminosity
of the source.

@@

Since the illumination is just a polynomial in $x$, $y$, and $z(x, y)$, we

@@

Recalling the structure of the basis (c.f. Appendix~\ref{app:starry}),

@@

    \BF{i}(b, \theta) & =
    I_0

@@

    \BF{I}(b, \theta) & =
    I_0

@@

@@

We may now re-write Equations~(\ref{eq:rTA1Ry}) and (\ref{eq:sTARRy}) to
account for this illumination transformation. The flux outside of occultation
is now given by
%
\begin{align}
    \label{eq:rTIA1RRy}
    f = \rT \BF{I} \BF{A_1} \BF{R}'' \BF{R} \BF{y}
    \quad,
\end{align}
%
and the flux during an occultation by
%
\begin{align}
    \label{eq:sTA2IA1RRy}
    f = \sT \BF{A_2} \BF{I} \BF{A_1} \BF{R}' \BF{R} \BF{y}
    \quad.
\end{align}
%
Two notes about these equations. First, we introduced a new rotation matrix
$\BF{R}''$ in Equation~(\ref{eq:rTIA1RRy}), which rotates the problem so that
the semi-major axis of the terminator is aligned with the $x$-axis; as will
become clear in \S\ref{sec:case-0} below, this greatly simplifies the
integration step. Second, in the derivation of Equation~(\ref{eq:sTA2IA1RRy})
we used the fact that $\BF{A} = \BF{A_2} \BF{A_1}$
\citep[c.f. Equation~14 in][]{Luger2019}, where $\BF{A_1}$ transforms from
the spherical harmonic basis $\by$ to the polynomial basis $\bp$, and
$\BF{A_2}$ transforms from $\bp$ to the Green's basis $\bg$.

Figure~\ref{fig:frames} summarizes the transformations involved in the two
equations above. Starting on the right with a map vector $\BF{y}$ in
the spherical harmonic basis $\by$, defined in some observer-independent frame
$\mathcal{F}_0$, we first rotate it via $\BF{R}$ to the sky frame
$\mathcal{F}_\mathrm{sky}$, in which orientation the body is viewed by the
observer. If there is no occultation (upper branch of the figure), we then
rotate the map once more via $\BF{R}''$ to the integration frame
$\mathcal{F}_\mathrm{int}$, in which the terminator is parallel to the
$x$-axis. We then apply $\BF{A_1}$ to change basis to $\bp$, apply the
illumination transform $\BF{I}$, and finally dot in the solutions to the
surface integrals $\rT$. If, on the other hand, an occultor is present,
we rotate the map from $\mathcal{F}_\mathrm{sky}$ via $\BF{R}'$ to the frame
$\mathcal{F}_\mathrm{greens}$, in which the occultor lies along the
$+y$-axis. We then apply $\BF{A_1}$ to change basis to $\bp$ and $\BF{I}$
to weight the map by the illumination as above. Finally, we change basis
via $\BF{A_2}$ to the Green's basis, in which we compute and dot the
integrals $\sT$.

In \citet{Luger2019}, the crux of the problem was to compute the terms in the
vectors $\sT$ and $\rT$, which are surface integrals over
the region of the body that is visible to the observer
(see Figure 2 in that paper). Here, these integrals are significantly
more difficult, because they involve not only integration along the
limb of the body and of a possible occultor, but also along the
elliptical day/night terminator.

@@

\subsection{Problem Setup}
\label{sec:setup}
%

Figure~\ref{fig:cases} shows the
eight families of cases involving an occultation of an illuminated body by
a spherical occultor. Each of these cases correspond to distinct ways in
which the limb of the occultor can intersect with the limb of the occulted
body and its terminator; together, these cases encompass all possible
occultation configurations, for any illumination angle, occultor size, and
occultor position. In the next three sections, we present the solution for the
$\sT$, and hence for the total visible flux, for each of these cases.

\section{The Solution}
\label{sec:solution}
%
\subsection{Case 0}
\label{sec:case-0}
%
Before we tackle configurations involving occultations, we must address the
simpler problem of computing the total visible flux from an unocculted
body in reflected light (see Figure~\ref{fig:illum}). This problem was
originally solved by \citet{Haggard2018} and subsequently adapted to the
\starry formalism in \citet{Luger2019b}, but for completeness we present
the detailed solution in Appendix~\ref{app:case0}. We will refer to the
solution vector for this case as $\sT_0$ (Equation~\ref{eq:sT0}).

\subsection{Cases 1--4}
\label{sec:cases-1-4}
%
Cases 1--4 (see Figure~\ref{fig:cases}) involve configurations in which the
occultor does not intersect with
the terminator of the occulted body, and are therefore fairly
straightforward to solve.
%
Case 1 corresponds to any complete occultation of the body, so its
solution vector is trivial:
%
\begin{align}
    \label{eq:sT1}
    \sT_1 = \BS{0}
    \quad.
\end{align}
%
Case 2 involves any occultation in which the occultor blocks \emph{only} the
night side of the body (regardless of whether or not it intersects with the
limb of the body). Since the night side intensity is zero everywhere, this case
is also trivial, as the integration is the same as in case 0:
%
\begin{align}
    \label{eq:sT2}
    \sT_2 = \sT_0(b, \theta)
    \quad.
\end{align}
%
Case 3 corresponds to occultations in which the occultor blocks \emph{all} of
the night side of the body and \emph{some} of the day side. In this
configuration, the unocculted part of the disk consists only of dayside.
Since we have no intersections with the terminator to worry about,
we may compute the total flux using the \starry formalism from
\citet{Luger2019}, provided we weight the intensity map by the illumination
field:
%
\begin{align}
    \label{eq:sT3}
    \sT_3 = \sT_\star(b_o, r_o) \BS{\Psi}(b, \theta, d_s)
    \quad,
\end{align}
%
where $\sT_\star$ is the usual \starry solution vector
\citep[Equation~26 in][]{Luger2019} and $\BS{\Psi}$ is an illumination
matrix (Appendix~\ref{app:case3}).
%
Finally, case 4 involves any occultation in which the occultor blocks
\emph{only} the day side of the body (regardless of whether or not it
intersects with the limb).
%
\begin{align}
    \label{eq:sT4}
    \sT_4 = \sT_\star(b_o, r_o) + \sT_0(-b, \theta + \pi)
    \quad.
\end{align}
%

% case 1: 0
% case 2: s0
% case 3: sTe * I
% case 4: sTe * I + ~sT0

\subsection{Cases 5--8}
\label{sec:cases-5-8}
%
Cases 5--8 (see Figure~\ref{fig:cases}, Figure~\ref{fig:geometry}).

\section{Performance}
\label{sec:performance}
%
See Figure~\ref{fig:speed}.
%
\begin{figure}[h!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/speed.pdf}
        \oscaption{speed}{%
            Evaluation time for the starry algorithm.
            \label{fig:speed}
        }
    \end{centering}
\end{figure}

\section{Case 0}
\label{app:case0}
%
Our task is to compute the solution vector for this
configuration, which we will denote $\BF{s}^\top_0$.
Since in this case there is no occultor, it is
more convenient to perform the integration in a frame $\mathcal{F}''$ where the
semi-major axis of the terminator is aligned with the $x$-axis
(see Figure~\ref{fig:illum}); let us denote the matrix that rotates us
from $\mathcal{F}'$ to $\mathcal{F}''$ as $\BF{R}''$.
It is also far easier to perform the integration
in the \emph{polynomial basis} $\bp$
\citep[Equation 7 in][]{Luger2019}:
%
\begin{align}
    \tilde{p}_{l,m}(x, y) & =
    \begin{dcases}
        x^\frac{\mu}{2} y^\frac{\nu}{2}
         & \qquad \mu, \nu \, \mathrm{even}
        \\[1em]
        x^\frac{\mu-1}{2} y^\frac{\nu-1}{2} z(x, y)
         & \qquad \mathrm{otherwise} \quad,
    \end{dcases}
\end{align}
%
where $\bp$ is again ordered such that the component at
index $n$ is $\tilde{p}_{l,m}$, with $l$ and $m$ given by
Equation~(\ref{eq:lm}).
Now, if $\BF{r}^\top$ is the solution to the surface integrals in the
polynomial basis in $\mathcal{F}''$,
we may compute the desired solution vector in the Green's basis from
%
\begin{align}
    \label{eq:sT0}
    \BF{s}^\top_0 & = \BF{r}^\top \BF{A_1} \BF{R}'' \BF{A}^{-1}
    \quad,
\end{align}
%
where $\BF{A_1}$ \citep[Equation B11 in][]{Luger2019}
transforms the solution into the spherical harmonic basis so it can
be rotated out of the integration frame $\mathcal{F}''$ via $\BF{R}''$, and
$\BF{A}^{-1}$ \citep[Equation B13 in][]{Luger2019} transforms the
result into the Green's basis (in which $\sT$ is defined).

Our task is thus to compute $\BF{r}^\top$.
In frame $\mathcal{F}''$, the body sits at the origin and is
illuminated by a point source in the
$y-z$ plane at coordinates $(0, y_s, z_s)$ as in Figure~\ref{fig:illum}.
The day/night terminator is a half-ellipse whose semi-major axis
is unity and is aligned with the $x$-axis. The semi-minor axis is given
by $b = -\nicefrac{z_s}{\sqrt{y_s^2 + z_s^2}}$, where $b > 0$ corresponds to
a half-ellipse that is concave down and $b < 0$ to one that is concave up.
It is straightforward to show
that the illumination at a point $(x, y)$ on the projected disk is
given by
    \Psi(b; x, y) & =
    \begin{dcases}
        b_cy - bz(x, y) &
        \quad\quad\quad\quad\quad\quad\quad\quad\quad\quad
        y \geq b \sqrt{1 - x^2}
        \\
        0               &
        \quad\quad\quad\quad\quad\quad\quad\quad\quad\quad
    \end{dcases}
    \quad ,
    \label{eq:illum}
where $b_c = \sqrt{1 - b^2}$.
The elements of the solution vector may then be computed from

@@

    r_{l, m}(b) & =

@@

    \tilde{p}_{n(\mu,\nu)}(x, y)
    \Psi(b; x, y)

@@

This is the integral of the illumination-weighted intensity of each
term in the polynomial basis over the projected visible dayside of the
body.

@@

Equation~(\ref{eq:rT}) may be solved analytically in terms of purely
trigonometric and algebraic functions of $b$:

@@

    r_{l, m}(b) & =

@@

@@

    \label{eq:IJK}
    I_{j}(b) &= \int_b^1 a^j \sqrt{1 - a^2} \dd a

@@

        I_{0}(b) & = \frac{\arccos(b) - bb_c}{2}

@@

        I_{1}(b) & = \frac{b_c^3}{3}

@@

    I_{j}(b) &= \frac{b^n b_c^3 + (j - 1) I_{j - 2}(b)}{j + 2}

@@

\section{Case 3}
\label{app:case3}
Hello.

\section{Case 4}
\label{app:case4}
Hello.

\section{Cases 5--8}
\label{app:cases-5-8}
Hello.

>>>>

% Shorthand for this paper
\usepackage{xifthen}
\newcommand{\BF}[1]{\ensuremath{\mathbf{#1}}}
\newcommand{\BS}[1]{\ensuremath{\boldsymbol{#1}}}
\newcommand{\dd}{\ensuremath{\mathrm{d}}}
\newcommand{\STARRYQUADPOINTS}{100\xspace}
\newcommand{\bkappa}{\BS{\kappa}}
\newcommand{\blambda}{\BS{\lambda}}
\newcommand{\bxi}{\BS{\xi}}
\newcommand{\vmax}{{v_\mathrm{max}}}
\newcommand{\kapint}[1]{%
\sum_{i = 0}^{\frac{N - 1}{2}}
\int\limits_{\frac{1}{2}\kappa_{2i}}^{\frac{1}{2}\kappa_{2i+1}}
#1
\dd\varphi
}
\newcommand{\lamint}[1]{%
\sum_{i = 0}^{\frac{N - 1}{2}}
\int\limits_{\frac{1}{2}\lambda_{2i}}^{\frac{1}{2}\lambda_{2i+1}}
#1
\dd\varphi
}
\newcommand{\coshalfkap}[1][]{%
\ifthenelse{%
    \equal{#1}{}
}{
    \cos\left(\frac{\bkappa}{2}\right)
}{
    \cos^{#1}\left(\frac{\bkappa}{2}\right)
}}
\newcommand{\sinhalfkap}[1][]{%
\ifthenelse{%
    \equal{#1}{}
}{
    \sin\left(\frac{\bkappa}{2}\right)
}{
    \sin^{#1}\left(\frac{\bkappa}{2}\right)
}}
\newcommand{\DE}{\Delta \BS{E}(k^2, \bkappa)}
\newcommand{\DF}{\Delta \BS{F}(k^2, \bkappa)}
\newcommand{\sgn}{{\mathrm{sgn}}}
\newcommand{\xhat}{\ensuremath{\mathbf{\hat{x}}}\xspace}
\newcommand{\yhat}{\ensuremath{\mathbf{\hat{y}}}\xspace}
\newcommand{\zhat}{\ensuremath{\mathbf{\hat{z}}}\xspace}
\newcommand{\sT}{\ensuremath{\mathfrak{s}^\top}}
\newcommand{\rT}{\ensuremath{\mathfrak{r}^\top}}
\newcommand{\sTe}{\ensuremath{\BF{s}^\top}}
\newcommand{\rTe}{\ensuremath{\BF{r}^\top}}
%
\newcommand{\bg}{\ensuremath{\tilde{\BF{g}}}}
\newcommand{\bp}{\ensuremath{\tilde{\BF{p}}}}
\newcommand{\by}{\ensuremath{\tilde{\BF{y}}}}

@@

%
\section{The Problem}
\label{sec:the-problem}
%
\subsection{Review of the \starry algorithm in emitted light}
\label{sec:starry-review}
%
Without loss of generality, assume the body whose flux we wish to compute
has radius unity and sits at the origin of a right-handed Cartesian coordinate
system with the $x$-axis pointing to the right on the sky, the $y$-axis
pointing up on the sky, and the $z$-axis pointing out of the sky
toward the observer; denote this frame by $\mathcal{F}_0$. In $\mathcal{F}_0$,
the surface (emitted) intensity field of the body is described by the
spherical harmonic coefficient vector $\mathbf{y}$. Following
\citet{Luger2019}, when no occultor is present, we may compute the total
visible flux $f_0$ from this body as
%
\begin{align}
    \label{eq:rTA1Ry}
    f_0 = \rTe \BF{A_1} \BF{R} \BF{y}
    \quad,
\end{align}
%
where, from right to left, $\BF{R} = \BF{R}(i, \lambda, \vartheta)$
is a Wigner rotation matrix that rotates $\bvec{y}$ to the sky frame
$\mathcal{F}_\mathrm{sky}$ given the body's inclination $i$, obliquity
$\lambda$, and rotational phase $\vartheta$ (Equation~\ref{eq:R}),
%
$\BF{A_1}$ is the change-of-basis matrix from the spherical harmonic
basis $\by$ to the \emph{polynomial basis} $\bp$ in which the integrals
are computed (Equation~\ref{eq:A1}),
%
and $\rTe$ is the vector of solutions to the integral over
the projected visible disk of the body for each term in $\bp$
(Equation~\ref{eq:rTe}).
%
If instead an occultor of radius $r_o$ is located at position $(x_o, y_o)$,
we instead compute the visible flux $f$ from
%
\begin{align}
    \label{eq:sTARRy}
    f = \sTe \BF{A} \BF{R}' \BF{R} \BF{y}
    \quad,
\end{align}
%
where, as before, $\BF{R}$ rotates the body from $\mathcal{F}_0$
to $\mathcal{F}_\mathrm{sky}$,
%
$\BF{R}' = \BF{R}'(\omega)$ rotates the body on the plane
of the sky by an angle
$\omega = \nicefrac{\pi}{2} - \mathrm{arctan2}(y_o, x_o)$
into a frame $\mathcal{F}_\mathrm{greens}$ in which the
occultor lies along the $+y$-axis (Equation~\ref{eq:R'}),
%
$\BF{A}$ is the change-of-basis matrix from $\by$
to the \emph{Green's basis} $\bg$ in which the integrals are computed
(Equation~\ref{eq:A}),
%
and $\sTe = \sTe(b_o, r_o)$ is the vector of solutions to the integral over
the projected visible disk of the body for each term in $\bg$
(Equation~\ref{eq:sTe}), with $b_o = \sqrt{x_o^2 + y_o^2}$.
For more details, see Appendix~\ref{app:starry} and \citet{Luger2019}.

@@

body is illuminated by a point-like source of unit luminosity, in which case
the radiance at any

@@

of semi-major axis unity that is fully described by its (signed) semi-minor
axis,

@@

    b = -\frac{z_s}{r_s}

@@

where $r_s = \sqrt{x_s^2 + y_s^2 + z_s^2}$ is the distance to the source,

@@

$r_s \gg 1$,

@@

$\mathfrak{I}$ at a point $(x, y)$ on the projected disk of the body is given
by the function

@@

    \label{eq:Psi}
    \mathfrak{I}(b, \theta, r_s; x, y)&=
    \mathrm{max}\bigg( 0, I(b, \theta, r_s; x, y) \bigg)

@@

@@

    I(b, \theta, r_s; x, y) &= \frac{1}{4\pi r_s^2}
    \bigg(
    \bigg)

@@

with $b_c = \sqrt{1 - b^2}$ and $z(x, y) = \sqrt{1 - x^2 - y^2}$.

@@

Since $I$ is just a polynomial in $x$, $y$, and $z(x, y)$, we

@@

Recalling the structure of the basis (Equation~\ref{eq:p}),

@@

    \BF{i}(b, \theta, r_s) & =
    \frac{1}{4\pi r_s^2}

@@

    \BF{I}(b, \theta, r_s) & =
    \frac{1}{4\pi r_s^2}

@@

Note, importantly, that this weighting is valid only on the dayside
hemisphere (see Equation~\ref{eq:Psi}), as the operator $\BF{I}$ weights
points on the nightside by a \emph{negative} amount, which is clearly
unphysical. As we will see momentarily, we account for this by excluding the
nightside from the integration region in our flux integrals.

@@

We may now re-write Equations~(\ref{eq:rTA1Ry}) and (\ref{eq:sTARRy}) to
account for this illumination transformation. The flux outside of occultation
is now given by
%
\begin{align}
    \label{eq:rTIA1RRy}
    f_0 & =
    \mathfrak{r}^\top(b)
    \BF{I}(b, 0, r_s)
    \BF{A_1}
    \BF{R}'(-\theta)
    \BF{R}(i, \lambda, \vartheta)
    \BF{y}
    \quad,
\end{align}
%
and the flux during an occultation by
%
\begin{align}
    \label{eq:sTA2IA1RRy}
    f & =
    \mathfrak{s}^\top(b, \theta, b_o, r_o)
    \BF{A_2}
    \BF{I}(b, \theta, r_s)
    \BF{A_1}
    \BF{R}'(\omega)
    \BF{R}(i, \lambda, \vartheta)
    \BF{y}
    \quad.
\end{align}
%
A few notes about these equations are in order.
First, we now apply a rotation matrix $\BF{R}'(-\theta)$
(Equation~\ref{eq:R'}) to the unocculted case,
which rotates the body so the semi-major axis of the terminator is aligned
with the $x$-axis; as will become clear in \S\ref{sec:solution-no-occ} below,
this greatly simplifies the integration step. Note the corresponding change
in $\BF{I}$, which we call with $\theta = 0$.
%
Second, in the derivation of Equation~(\ref{eq:sTA2IA1RRy})
we used the fact that $\BF{A} = \BF{A_2} \BF{A_1}$
(Equation~\ref{eq:A}), where $\BF{A_1}$ transforms from
the spherical harmonic basis $\by$ to the polynomial basis $\bp$, and
$\BF{A_2}$ transforms from $\bp$ to the Green's basis $\bg$.
Finally, note that we replaced the integral vectors
$\rTe$ and $\sTe(b_o, r_o)$
with the vectors
$\mathfrak{r}^\top(b)$ and $\mathfrak{s}^\top(b, \theta, b_o, r_o)$,
respectively.
As we mentioned above, we must modify the integration limits to exclude the
nightside, where the weighting by $\BF{I}$ is unphysical.
The vectors $\mathfrak{r}^\top$ and $\mathfrak{s}^\top$ correspond to these
modified integrals, which we devote the rest of this paper to
computing.

Figure~\ref{fig:frames} summarizes the transformations involved in the two
equations above. Starting on the right with a map vector $\BF{y}$ in
the spherical harmonic basis $\by$, defined in some observer-independent frame
$\mathcal{F}_0$, we first rotate it via $\BF{R}$ to the sky frame
$\mathcal{F}_\mathrm{sky}$, in which orientation the body is viewed by the
observer. If there is no occultation (upper branch of the figure), we then
rotate the map once more via $\BF{R}'$ to the integration frame
$\mathcal{F}_\mathrm{int}$, in which the terminator is parallel to the
$x$-axis. We then apply $\BF{A_1}$ to change basis to $\bp$, apply the
illumination transform $\BF{I}$, and finally dot in the solutions to the
surface integrals $\rT$. If, on the other hand, an occultor is present,
we rotate the map from $\mathcal{F}_\mathrm{sky}$ via $\BF{R}'$ to the frame
$\mathcal{F}_\mathrm{greens}$, in which the occultor lies along the
$+y$-axis. We then apply $\BF{A_1}$ to change basis to $\bp$ and $\BF{I}$
to weight the map by the illumination as above. Finally, we change basis
via $\BF{A_2}$ to the Green's basis, in which we compute and dot the
integrals $\sT$.

@@

\section{The Solution: No Occultation}
\label{sec:solution-no-occ}
%
Before we tackle configurations involving occultations, we must address the
simpler problem of computing the total visible flux from an unocculted
body in reflected light (Equation~\ref{eq:rTIA1RRy}). This problem was
originally solved by \citet{Haggard2018} and subsequently by
\citet{Luger2019b}, but for completeness we present the detailed
derivation in the \starry formalism here.

As we discussed above, we perform the integration in a frame
$\mathcal{F}_\mathrm{int}$
in which the semi-major axis of the terminator is aligned with the
$x$-axis, with the illumination source at $y \ge 0$.
The solution vector may then be computed from

@@

    \rT(b) & =

@@

    \bp(x, y)

@@

which is identical to Equation~(20) in \citet{Luger2019} except for the
lower integration limit of the inner integral. The lower limit is now
the equation describing the terminator, which ensures we always exclude the
nightside from the integration region.

@@

For computational efficiency, in practice we compute the integral of the
intensity-weighted basis directly,
    \label{eq:rTI}
    \BS{\rho}^\top(b, r_s) & \equiv
    \rT(b) \mathbf{I}(b, 0, r_s)
                           & =
    \bp(x, y)
    \mathbf{I}(b, 0, r_s)
recalling that in frame $\mathcal{F}_\mathrm{int}$, $\theta = 0$ by
definition.
Equation~(\ref{eq:rTI}) may be solved analytically in terms of purely
trigonometric and algebraic functions of $b$. The component of $\BS{\rho}^\top$
at index $n$ is given by

@@

    \rho_n(b, r_s) & =
    \frac{1}{4\pi r_s^2}

@@

where we make use of the indices
    \label{eq:l-m-mu-nu}
    \mu & = l - m
    \nu & = l + m
    l   & = \floor*{\sqrt{n}}
    m   & = n - l^2 - l
as in \citet{Luger2019} and we define the helper functions

@@

    \label{eq:HJK}
    H_{j}(b) &= \int_b^1 a^j \sqrt{1 - a^2} \dd a

@@

        H_{0}(b) & = \frac{\arccos(b) - bb_c}{2}

@@

        H_{1}(b) & = \frac{b_c^3}{3}

@@

    H_{j}(b) &= \frac{b^n b_c^3 + (j - 1) H_{j - 2}(b)}{j + 2}

@@

Once $\BS{\rho}^\top$ is known, the observed flux is computed from
(c.f. Equation~\ref{eq:rTIA1RRy})
    \label{eq:f0}
    f_0 & =
    \BS{\rho}^\top(b, r_s)
    \BF{A_1}
    \BF{R}'(-\theta)
    \BF{R}(i, \lambda, \vartheta)
    \BF{y}

\section{The Solution: Occultation}
\label{sec:solution-occ}

Figure~\ref{fig:cases} shows the
eight families of cases involving an occultation of an illuminated body by
a spherical occultor. Each of these cases correspond to distinct ways in
which the limb of the occultor can intersect with the limb of the occulted
body and its terminator; together, these cases encompass all possible
occultation configurations, for any illumination angle, occultor size, and
occultor position. In the following sections, we present the solution for the
$\sT$, and hence for the total visible flux, for each of these cases.

\xxx{How do we determine which case we're modeling?}

\subsection{Cases 1--4}
\label{sec:cases-1-4}
%
Cases 1--4 (see Figure~\ref{fig:cases}) involve configurations in which the
occultor does not intersect with
the terminator of the occulted body, and are therefore fairly
straightforward to solve.
%
Case 1 corresponds to any complete occultation of the body, so the
solution for the flux is trivial:
%
\begin{align}
    \label{eq:sT1}
    f_1 = 0
    \quad.
\end{align}
%
Case 2 involves any occultation in which the occultor blocks \emph{only} the
night side of the body (regardless of whether or not it intersects with the
limb of the body). Since the night side intensity is zero everywhere, this case
is also trivial, as the flux is equal to the flux in the no occultation case
(Equation~\ref{eq:f0}):
%
\begin{align}
    \label{eq:sT2}
    f_2 = f_0
    \quad.
\end{align}
%
Case 3 corresponds to occultations in which the occultor blocks \emph{all} of
the night side of the body and \emph{some} of the day side. In this
configuration, the unocculted part of the disk consists only of dayside.
Since we have no intersections with the terminator to worry about,
we may compute the total flux using the \starry formalism from
\citet{Luger2019}, provided we weight the intensity map by the illumination
field:
%
\begin{proof}{}
    \label{eq:f3}
    f_3 = \sTe(b_o, r_o)
    \BF{A_2}
    \BF{I}(b, \theta, r_s)
    \BF{A_1}
    \BF{R}'(\omega)
    \BF{R}(i, \lambda, \vartheta)
    \BF{y}
    \quad.
\end{proof}
%
Finally, case 4 involves any occultation in which the occultor blocks
\emph{only} the day side of the body (regardless of whether or not it
intersects with the limb):
%
\begin{proof}{}
    \label{eq:sT4}
    f_4 = f_3 + \hat{f}_0
    \quad,
\end{proof}
%
where we define
%
\begin{proof}{}
    \label{eq:f0hat}
    \hat{f}_0 & =
    \BS{\rho}^\top(-b, r_s)
    \BF{A_1}
    \BF{R}'(-\theta - \pi)
    \BF{R}(i, \lambda, \vartheta)
    \BF{y}
    \quad.
\end{proof}

\subsection{Cases 5--8}
\label{sec:cases-5-8}
%
\xxx{Cases 5--8} (see Figure~\ref{fig:cases}, Figure~\ref{fig:geometry}).

\section{Performance}
\label{sec:performance}
%
\xxx{Performance!} See Figure~\ref{fig:speed}.
%
\begin{figure}[h!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/speed.pdf}
        \oscaption{speed}{%
            Evaluation time for the starry algorithm.
            \label{fig:speed}
        }
    \end{centering}
\end{figure}

\xxx{Work in progress below here.}

The \emph{polynomial basis} $\bp$
\citep[Equation 7 in][]{Luger2019}:
%
\begin{align}
    \tilde{p}_{l,m}(x, y) & =
    \begin{dcases}
        x^\frac{\mu}{2} y^\frac{\nu}{2}
         & \qquad \mu, \nu \, \mathrm{even}
        \\[1em]
        x^\frac{\mu-1}{2} y^\frac{\nu-1}{2} z(x, y)
         & \qquad \mathrm{otherwise} \quad,
    \end{dcases}
\end{align}
%
where $\bp$ is again ordered such that the component at
index $n$ is $\tilde{p}_{l,m}$, with $l$ and $m$ given by
Equation~(\ref{eq:lm}).
